Supporting information: Copulas and their potential for ecology

### 2019-06-16 SupportingInformation.Rmd
further edits, increasingly minor

\noindent The matrices from which root character states and changes 
across phylogeny branches were randomly chosen were generated as follows.
For extreme right-tail dependent noise, we first produced
a 1,000,000 by $2$ matrix, $m$, of 
independent standard-normal random draws. Then, each row of $m$ 
was identified for a first set of modifications randomly 
and independently with a $50\%$ chance; 
for those rows identified, every element of the row was replaced with the 
absolute value of the first element of the row (including the first element itself).
For other rows, every element in the row was replaced by the negative of its
own absolute value. This produces right-tail dependent noise, normally distributed
for each location. If left-tail dependent noise was desired, we took the negative of the
entire matrix. The moderately left-tail dependent matrix was based on a C copula 
with parameter chosen (using the `iRho` function in the `copula` package) so that
the Spearman correlation would be the same as for the extreme tail dependence 
datasets. The moderately right-tail dependent matrix and the symmetric tail dependence
matrix were constructed similarly, but using an SC copula and an N copula,
respectively.

>>>>

\noindent The matrices from which root character states and changes 
across phylogeny branches were randomly chosen were generated as follows.
For extreme right-tail dependent noise, we first produced
a 1,000,000 by $2$ matrix, $m$, filled with 2,000,000 
independent standard-normal random draws. Then, each row of $m$ 
was identified for a first set of modifications randomly 
and independently with a $50\%$ chance; 
for those rows identified, every element of the row was replaced with the 
absolute value of the first element of the row (including the first element itself).
For other rows, every element in the row was replaced by the negative of its
own absolute value. This produces right-tail dependent noise, normally distributed
for each of the two locations. 
If left-tail dependent noise was desired, we took the negative of the
entire matrix. The moderately left-tail dependent matrix was based on a C copula 
with parameter chosen (using the `iRho` function in the `copula` package) so that
the Spearman correlation would be the same as for the extreme tail dependence 
datasets. The moderately right-tail dependent matrix and the symmetric tail dependence
matrix were constructed similarly, but using an SC copula and an N copula,
respectively.
